\documentclass[review]{elsarticle}

\usepackage{lineno,hyperref}
\modulolinenumbers[5]

\journal{Nuclear Instruments and Methods B}

%%%%%%%%%%%%%%%%%%%%%%%
%% Elsevier bibliography styles
%%%%%%%%%%%%%%%%%%%%%%%
%% To change the style, put a % in front of the second line of the current style and
%% remove the % from the second line of the style you would like to use.
%%%%%%%%%%%%%%%%%%%%%%%

%% Numbered
%\bibliographystyle{model1-num-names}

%% Numbered without titles
%\bibliographystyle{model1a-num-names}

%% Harvard
%\bibliographystyle{model2-names.bst}\biboptions{authoryear}

%% Vancouver numbered
%\usepackage{numcompress}\bibliographystyle{model3-num-names}

%% Vancouver name/year
%\usepackage{numcompress}\bibliographystyle{model4-names}\biboptions{authoryear}

%% APA style
%\bibliographystyle{model5-names}\biboptions{authoryear}

%% AMA style
%\usepackage{numcompress}\bibliographystyle{model6-num-names}

%% `Elsevier LaTeX' style
\bibliographystyle{elsarticle-num}
%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\begin{frontmatter}

\title{Fluorescence yield for plastic scintillators after irradiation }


%% or include affiliations in footnotes:
\author[umd]{Zishuo Yang\corref{mycorrespondingauthor}}
\cortext[mycorrespondingauthor]{Corresponding author}
\ead{yangzs@terpmail.umd.edu}
\author[umd]{Alberto Belloni}
\author[umd]{Sarah C. Eno}
\author[eljen]{Charles Hurlbut}
\author[umd]{Geng Yuan Jeng}
\author[umd]{Yao Yao}




\address[umd]{Dept. Physics, U. Maryland, College Park MD 30742 USA}
\address[eljen]{Eljen Technology, 1300 W. Broadway, Sweetwater, Tx 79556 USA}


\begin{abstract}
The ratio of the fluorescence yield versus wavelength for plastic scintillators EJ-408 and EJ-260 before and after irradiation by a $\rm {^{60}Co}$ source for doses of 50, 30, 10, 4, and 2 Mrad at various dose rates and for different concentrations of the primary and secondary dopant.  While the nominal dopant concentration gives the highest light output prior to irradiation, a higher concentration is found to be optimal for irradiated plastics.
\end{abstract}

\begin{keyword}
plastic scintillator\sep fluorescence\sep radiation hardness\sep 
\end{keyword}

\end{frontmatter}

\linenumbers

\section{Introduction}
Organic scintillators (such as toluene, polystyrene, and naphthalene) containing wave-length shifting
additives in solution have long been popular elements in detectors used
in particle physics, nuclear physics, radiation safety, and heath physics applications  due to their high light output, low cost, fast response,
and versatility of physical construction. 
Plastic scintillators and wavelength shifters, including
wavelength shifting fibers, are currently available
from companies such as St. Gobain, Kuraray, and Eljen.
Prolonged exposure of plastic scintillator to
ionizing radiation has harmful effects: it can increase
light self-absorption (yellowing) and  decrease
initial light yield.  
In this paper, we present measurements of ratio of the light output before and after irradiation
for two different types of plastic scintillator manufactured by Eljen corporation, EJ-408 and EJ-260, before and after irradiation by a $\rm {^{60}Co}$ source for doses of 50, 30, 10, 4, and 2 Mrad at various dose rates and for different concentrations of the primary and secondary dopant.

The induced attentuation length in plastic scintillators has been the study of extensive studies \cite{34504}, \cite{Wick1991472}, \cite{289295},
\cite{173180},\cite{467829},\cite{Wulkop1995141},\cite{173178}.  Especially, the presense of oxygen plays an important role.  As discussed 
in \cite{Wulkop1995141}, the presense of oxygen
increases the number of migration mechanisms for the radicals produced during irradiation.  The diffusion of oxygen into the scintillator
provides a mechanism for radiation damage to depend not only on dose, but also on time and on dose rate.  Simulations based on oxygen diffusion have been shown
to reproduce time dependence of the induced attentuation length in scintillators based on polystyrene and PMMA\cite{Wick1991472}.  
They show that the penetration depth of oxygen into the substrate
depends on the dose rate, presumably because interactions
of the oxygen with radicals affects its ability to diffuse.  
At lower dose rates, oxygen penetrates
more deeply.  Because of the importance of the interaction
of oxygen with radicals, this can lead to dose rate effects
for radiation damage.  They also show that the recovery of the
induced self absorption after irradiation (bleaching)
is consistent with
oxygen diffusion.  They show that there is little bleaching
without oxygen, and that a very large number of color centers
form if there is no oxygen, although the permanent damage after
bleaching (exposure to oxygen after the radiation) is slightly
larger if there is oxygen.






\section{Measurements}
Both EJ-408 and EJ-260 have 


\section{Conclusions}

\section{Acknowledgements}
The authors would like to thank Neil Blough and Anna Pla-Dalmau for advice on taking fluorescence measurements, and Blough for the use of his machine.  This work was supported in part by U.S. Department of Energy Grant YYYYY.

\section*{References}

\bibliography{afluorescence}

\end{document}